\documentclass[12pt]{article}

\begin{document}
    \large{Scenario’s (reveal each scenario separately)}
\begin{enumerate}
    \item First impressions
    \begin{enumerate}
        \item Briefly describe your experience level using the internet.
        \item Look at the site homepage for 2 seconds:
        \item Have you seen this site before?
        \item Just from looking briefly at this site, what kinds of information do you think you could get from this site? Please be specific.
    \end{enumerate}
    \item Find out more \\ You have a grandparent who has been diagnosed with Alzheimer's disease, while doing research on this topic you came across this which might suit your grandparent, How would you find out more information to find out if they can take part in this study?
    \newpage
    \item Form answers
    \begin{enumerate}
        \item Do you accept the "Fair Processing Notice?": YES
        \item Please select who would participate in the Study?: DEPENDENT
        \item Have you been diagnosed probable Alzheimer's disease: YES
        \item Are you aged between 50 to 85?: YES
        \item Do you suffer from depression?: NO
        \item Are you in general good health?: YES
        \item Do you require continuous nursing care?: NO
        \item Can you swallow medicine in a liquid form?: YES
        \item Have you been admitted to hospital within the last 4 weeks?: NO
        \item Have you been diagnosed with schizophrenia?: NO
        \item Have you been diagnosed with bipolar disorder?: NO
    \end{enumerate}
    \item Do They live near? \\ You've found out that your grandparent is eligible for the study, however they live Orlando, Florida in The United States. You need to find out if there is a clinic near them.
\end{enumerate}

\end{document}